Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-05 paper/aldebaran.tex
phrasing

In order to confirm the oscillations detected in the archival data, we used the Hertzsprung SONG telescope \cite{2017ApJ...836..142G} to conduct high time cadence follow-up observations. These were carried out in the highest resolution mode (R$\approx\,110.000$)
with an integration time of 30s, between 27 September 
2016 and  12 January 2017. During this time we attempted to obtain at least one 
visit per available night, for a total of 254 epochs over the campaign. The spectra were
extracted using the SONG pipeline (see \cite{2017ApJ...836..142G}). SONG employs an iodine cell for
precise wavelength calibration and the velocities were determined using the $\it iSONG$
software following the same procedures as described in \cite{2017ApJ...836..142G}.   The typical
velocity precision per visit is 2.5$m\,s^{-1}$ allowing us to easily detect the oscillations
which displays a peak-to-peak amplitude of $\approx \, 170 \, \rm m \, s^{-1}$. $\bf Figure XX$ show
the radial velocities obtained -- oscillations are easily visible as well as a long-term
trend. This is probably due to the a manifestation of the planetary companion reported by
\cite{Hatzes2015}.

>>>>

In order to confirm the oscillations detected in the archival data, we used the Hertzsprung SONG telescope \cite{2017ApJ...836..142G} to conduct high time cadence follow-up observations. These were carried out in the highest resolution mode (R$\approx\,110.000$)
with an integration time of 30s, between 27 September 
2016 and  12 January 2017. During this time we attempted to obtain at least one 
visit per available night, for a total of 254 epochs over the campaign. The spectra were
extracted using the SONG pipeline (see \cite{2017ApJ...836..142G}). SONG employs an iodine cell for
precise wavelength calibration and the velocities were determined using the $\it iSONG$
software following the same procedures as described in \cite{2017ApJ...836..142G}.   The typical
velocity precision per visit is 2.5$m\,s^{-1}$ allowing us to easily detect the oscillations
which displays a peak-to-peak amplitude of $\approx \, 170 \, \rm m \, s^{-1}$. $\bf Figure XX$ show
the radial velocities obtained -- oscillations are easily visible as well as a long-term
trend, probably due to the planetary companion.
